Lexicalized Domain Representations for Neural Machine Translation

### 2019-05-17 2019/emnlp/sparse.tex
transformer table
rnn table

\begin{table*}[!h]
\begin{center}
\scalebox{0.81}{
\begin{tabular}{|l|ccc|ccc||c|}
\hline
Model & EMEA & EPPS & ECB & khreshmoi & newstest & iwslt & Avg. \\
\hline
\multicolumn{8}{l}{English$\rightarrow$French} \\
\hline
$Mixed$ & 67.69 $_{47.60}$ & 37.50 & 53.49 & 34.86 & 28.56 & 25.70 & avg \\
\hline
$FT_{EMEA}$ & 76.77 $_{49.43}$ & 17.16 & 11.99 & 29.58 & 11.64 & 11.10 & avg \\
$FT_{EPPS}$ & 20.86 $$ & 37.04 & 24.53 & 31.86 & 28.33 & 11.10 & avg \\
$FT_{ECB}$   & 26.93 & 27.09 & 56.52 & 22.04 & 17.51 & 13.99 & avg \\
\hline
$DC$ & 67.87 $_{45.42}$ & 37.31 & 54.14 & 33.63 & 26.52 & 24.81 & avg\\
\hline
$LDR_{oracle}$   & 74.26 $_{49.90}$ & 37.67 & 54.07 & 33.85 & 28.11 & 25.70 & avg \\
$LDR_{generic}$ & 73.97 $_{49.54}$ & 37.81 & 53.67 & 34.17 & 28.11 & 25.70 & avg \\
$LDR_{rnn}$ & EMEA & EPPS & ECB & khreshmoi & newstest & iwslt & avg \\
$LDR_{wrong}$ & 72.95 $_{49.78}$ & 37.62 & 53.35 & khreshmoi & newstest & iwslt & avg\\
\hline
\multicolumn{8}{l}{English$\rightarrow$German} \\
\hline
$Mixed$ & 64.57 $_{42.99}$ & 26.47 & 68.67 & 21.77 & 17.04 & 18.85 & avg \\
\hline
$FT_{EMEA}$ & 68.35 $$ & 17.02 & 32.87 & 21.15 & 11.21 & 13.49 & avg\\
$FT_{EPPS}$ & 36.19 & 26.29 & 40.71 & 19.67 & 16.47 & 19.24 & avg \\
$FT_{ECB}$   & 24.72 & 18.36 & 74.05 & 11.31  & 10.8 & 11.00 & avg \\
\hline
$DC$ & 63.48 $_{42.98}$ & 26.27 & 66.95 & 21.45 & 16.45 & 18.78 & avg \\
\hline
$LDR_{oracle}$ & 70.9 $_{46.12}$ & 26.30 & 68.9 & 21.42 & 16.57 & 18.82 & avg\\
$LDR_{generic}$ & 70.86 $_{45.60}$ & 26.14 & 68.59 & 21.95 & 16.57 & 18.82 & avg\\
$LDR_{rnn}$ & EMEA & EPPS & ECB & khreshmoi & newstest & iwslt & avg \\
$LDR_{wrong}$ & 69.51 $_{43.50}$ & 26.31 & 66.86 & khreshmoi & newstest & iwslt & avg \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BPE-detokenized BLEU scores for the Transformer architecture over test sets.}
\end{table*}

\begin{table*}
\begin{center}
 \begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EMEA non-included & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & newstest 2014 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 64.57 & 42.99 & 26.47 & 68.67 & 21.77 & 23.50 & 13.9 & 17.04 & 18.85 \\
 \hline
 EMEA-finetuned & 68.35 & & 17.02 & 32.87 & 21.15 & 15.94 & 8.92 & 11.21 & 13.49 \\
 \hline
 EPPS-finetuned & 36.19 & & 26.29 & 40.71 & 19.67 & 23.69 & 14.08 & 16.47 & 19.24 \\
 \hline
 ECB-finetuned & 24.72 & & 18.36 & 74.05 & 11.31 & 16.64 & 9.11 & 10.8 & 11.0 \\
 \hline
 Sparse(1) & 70.9 & 46.12 & 26.30 & 68.9 & 21.42 & 23.73 & 13.99 & 16.57 & 18.82 \\
 \hline
 Sparse(2) & 70.86 & 45.6 & 26.14 & 68.59 & 21.95 & 23.79 & 13.99 & 16.57 & 18.82 \\
 \hline
 Sparse (3) &  &  &  &  &  &  &  &  & \\
 \hline
 Sparse (4) & 69.51 & 43.5 & 26.31 & 66.86 &  &  &  &  & \\
 \hline
 Domain Control & 63.48 & 42.98 & 26.27 & 66.95 & 21.45 & 23.95 & 13.94 & 16.45 & 18.78  \\
 \hline
\end{tabularx}
\end{center}
\caption{BLEU score for Transformer in language pair English - German. Notations are same as Table~\ref{tab:1}}
\label{tab:2}
\end{table*}

\begin{table*}
\begin{center}
 \begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EMEA non-included & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & newstest 2014 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 65.42 & 45.11 & 34.7 & 51.38 & 29.27 & 28.95 & 17.82 & 22.21 & 21.63 \\
 \hline
 EMEA-finetuned  & 72.06 & & 18.62 & 16.78 & 25.88 & 13.38 & 9.26 & 10.94 & 5.73 \\
 \hline
 EPPS-finetuned & 35.47 & & 34.61 & 39.56 & 27.11 & 28.8 & 17.3 & 21.85 & 20.61 \\
 \hline
 ECB-finetuned & 21.93 & & 22.6 & 51.53 & 14.74 & 20.23 & 9.74 & 12.10 & 10.47 \\
 \hline
 Sparse (1) & 71.73 & 46.3 & 35.21 & 50.91 & 29.62 & 29.05 & 17.92 & 23.00 & 20.96 \\
 \hline
 Sparse (2) & 70.59 & 46.37 & 35.22 & 49.68 & 29.51 & 29.32 & 17.92 & 23.00 & 20.96 \\
 \hline
 Sparse (3) &  &  &  &  & &  &  &  & \\
 \hline
 Sparse (4) & 62.1 & 43.29 & 34.17 & 48.79 &  &  &  &  & \\
 \hline
 Domain Control & 68.26 & 43.76 & 35.13 & 50.09 & 27.86 & 29.34 & 16.25 & 20.95 & 21.16 \\
 \hline
 WDCMT (conditional GRU) & 68.76 & 45.29 & 35.71 & 52.75 & 32.03 & 29.81 & 19.58 & 24.63 & 23.28 \\
 \hline 
\end{tabularx}
\end{center}
\caption{bpe-detokenized BLEU score for Recurrent network architecture on language pair English-French. Notations as same as figure \ref{tab:1} except that other models from WDCMT of \cite{Zeng18multidomain} use Bidirectional-LSTM}
\label{tab:3}
\end{table*}

\begin{table*}
\begin{center}
 \begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EMEA non-included & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & newstest 2014 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 57.37 & 37.94 & 23.1 & 63.54 & 17.39 & 20.65 & 10.69 & 11.51 & 14.29 \\
 \hline
 EMEA-finetuned & 65.64 & & 12.36 & 15.93 & 15.38 & 11.1 & 5.54 & 6.22 & 7.6 \\
 \hline
 EPPS-finetuned & 24.9 & & 22.98 & 26.26 & 13.55 & 20.95 & 10.58 & 11.33 & 14.32 \\
 \hline
 ECB-finetuned & 41.8 & & 15.97 & 71.07 & 10.77 & 14.67 & 7.06 & 7.66 & 8.07 \\
 \hline
 Sparse (1) & 63.43 & 40.04 & 22.66 & 64.4 & 16.99 & 20.63 & 10.89 & 11.45 & 14.26 \\
 \hline
 Sparse (2) & 63.27 & 39.75 & 22.62 & 63.7 & 17.26 & 20.69 & 10.89 & 11.45 & 14.26 \\
 \hline
 Sparse (3) &  &  &  &  & &  &  &  & \\
 \hline
 Sparse (4) & 56.84 & 37.05 & 22.06 & 61.66 &  &  &  &  & \\
 \hline
 Domain Control & 62.53 & 39.25 & 23.74 & 65.71 & 16.88 & 21.85 & 9.24 & 11.15 & 14.97 \\
 \hline
 WDCMT (conditional GRU) & 64.05 & 38.54 & 22.82 & 67 & 15.94 & 20.57 & 10.15 & 11.45 & 13.66 \\
 \hline 
\end{tabularx}
\end{center}
\caption{BLEU score for Recurrent network on language pair English - German. The notation is same as figure \ref{tab:3}}
\label{tab:4}
\end{table*}

>>>>

\begin{table*}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|ccc|ccc||c|}
\hline
Model & EMEA & EPPS & ECB & khreshmoi & newstest2014 & iwslt2010 & Avg. \\
\hline
\multicolumn{8}{l}{English$\rightarrow$French} \\
\hline
$Mixed$ & 67.69 $_{47.60}$ & 37.50 & 53.49 & 34.86 & 28.56 & 25.70 & avg \\
\hline
$FT_{EMEA}$ & 76.77 $_{49.43}$ & 17.16 & 11.99 & 29.58 & 11.64 & 11.10 & avg \\
$FT_{EPPS}$ & 20.86 $$ & 37.04 & 24.53 & 31.86 & 28.33 & 11.10 & avg \\
$FT_{ECB}$   & 26.93 & 27.09 & 56.52 & 22.04 & 17.51 & 13.99 & avg \\
\hline
$DC$ & 67.87 $_{45.42}$ & 37.31 & 54.14 & 33.63 & 26.52 & 24.81 & avg\\
\hline
$LDR_{oracle}$   & 74.26 $_{49.90}$ & 37.67 & 54.07 & 33.85 & 28.11 & 25.70 & avg \\
$LDR_{generic}$ & 73.97 $_{49.54}$ & 37.81 & 53.67 & 34.17 & 28.11 & 25.70 & avg \\
$LDR_{rnn}$ & EMEA & EPPS & ECB & khreshmoi & newstest & iwslt & avg \\
$LDR_{wrong}$ & 72.95 $_{49.78}$ & 37.62 & 53.35 & khreshmoi & newstest & iwslt & avg\\
\hline
\multicolumn{8}{l}{English$\rightarrow$German} \\
\hline
$Mixed$ & 64.57 $_{42.99}$ & 26.47 & 68.67 & 21.77 & 17.04 & 18.85 & avg \\
\hline
$FT_{EMEA}$ & 68.35 $$ & 17.02 & 32.87 & 21.15 & 11.21 & 13.49 & avg\\
$FT_{EPPS}$ & 36.19 & 26.29 & 40.71 & 19.67 & 16.47 & 19.24 & avg \\
$FT_{ECB}$   & 24.72 & 18.36 & 74.05 & 11.31  & 10.8 & 11.00 & avg \\
\hline
$DC$ & 63.48 $_{42.98}$ & 26.27 & 66.95 & 21.45 & 16.45 & 18.78 & avg \\
\hline
$LDR_{oracle}$ & 70.9 $_{46.12}$ & 26.30 & 68.9 & 21.42 & 16.57 & 18.82 & avg\\
$LDR_{generic}$ & 70.86 $_{45.60}$ & 26.14 & 68.59 & 21.95 & 16.57 & 18.82 & avg\\
$LDR_{rnn}$ & EMEA & EPPS & ECB & khreshmoi & newstest & iwslt & avg \\
$LDR_{wrong}$ & 69.51 $_{43.50}$ & 26.31 & 66.86 & khreshmoi & newstest & iwslt & avg \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BPE-detokenized BLEU scores for the Transformer architecture over test sets.}
\end{table*}

\begin{table*}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|ccc|ccc||c|}
\hline
Model & EMEA & EPPS & ECB & khreshmoi & newstest2014 & iwslt2010 & Avg. \\
\hline
\multicolumn{8}{l}{English$\rightarrow$French} \\
\hline
$Mixed$               & 65.42 $_{45.11}$ & 34.7 & 51.38 & 29.27 & 22.21 & 21.63 & avg \\
\hline
$FT_{EMEA}$     & 72.06 $$ & 18.62 & 16.78 & 25.88 & 10.94 & 5.73 & avg \\
$FT_{EPPS}$      & 35.47 $$ & 34.61 & 39.56 & 27.11 & 21.85 & 20.61 & avg \\
$FT_{ECB}$        & 21.93 $$ & 22.6 & 51.53 & 14.74 & 12.10 & 10.47 & avg \\
\hline
$DC$                   & 68.26 $_{43.76}$ & 35.13 & 50.09 & 27.86 & 20.95 & 21.16 & avg \\
 \hline
$WDCMT$           & 68.76 $_{45.29}$ & 35.71 & 52.75 & 32.03 & 24.63 & 23.28 & avg \\
\hline
$LDR_{oracle}$   & 71.73 $_{46.30}$ & 35.21 & 50.91 & 29.62 & 23.00 & 20.96 & avg\\
$LDR_{generic}$ & 70.59 $_{46.37}$ & 35.22 & 49.68 & 29.51 & 23.00 & 20.96 & avg\\
$LDR_{rnn}$        & EMEA & EPPS & ECB & khreshmoi & newstest & iwslt & avg\\
$LDR_{wrong}$   & 62.1 $_{43.29}$ & 34.17 & 48.79 & khreshmoi & newstest & iwslt & avg \\
\hline
\multicolumn{8}{l}{English$\rightarrow$German} \\
\hline
$Mixed$               & 57.37 $_{37.94}$ & 23.1 & 63.54 & 17.39 & 11.51 & 14.29 & avg\\
\hline
$FT_{EMEA}$      & 65.64 $$ & 12.36 & 15.93 & 15.38 & 6.22 & 7.6  & avg\\
$FT_{EPPS}$       & 24.90 $$ & 22.98 & 26.26 & 13.55 & 11.33 & 14.32 & avg \\
$FT_{ECB}$         & 41.8 $$ & 15.97 & 71.07 & 10.77 & 7.66 & 8.07 & avg\\
\hline
$DC$                    & 62.53 $_{39.25}$ & 23.74 & 65.71 & 16.88 & 11.15 & 14.97 & avg\\
\hline
WDCMT               & 64.05 $_{38.54}$ & 22.82 & 67.00 & 15.94 & 11.45 & 13.66 & avg\\
\hline
$LDR_{oracle}$   & 63.43 $_{40.04}$ & 22.66 & 64.40 & 16.99 & 11.45 & 14.26 & avg\\
$LDR_{generic}$ & 63.27 $_{39.75}$ & 22.62 & 63.70 & 17.26 & 11.45 & 14.26 & avg\\
$LDR_{rnn}$        & EMEA & EPPS & ECB & khreshmoi & newstest & iwslt & avg\\
$LDR_{wrong}$   & 56.84 $_{37.05}$ & 22.06 & 61.66 & khreshmoi & newstest & iwslt & avg \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BPE-detokenized BLEU scores for the RNN architecture over test sets.}
\end{table*}
